---
title: "Iowa State COVID-19 Tracking and Analysis"
author: "Ball, Jeremy T."
output:
  html_document:
    toc: TRUE
---

This notebook will be used to capture analysis work for the purpose of planning mission critical resources to combat COVID-19 within IA.

First thing we do is pull in a new daily snapshot of US daily tracking data.

```{r message=FALSE, warning=FALSE, include=FALSE}
library(httr)
library(jsonlite)
library(ggplot2)
library(dplyr)

states_daily.url <- "https://covidtracking.com/api/states/daily"
us_daily.url <- "https://covidtracking.com/api/us/daily"

states_daily <- GET(states_daily.url)
states_daily.text <- content(states_daily, "text")
states_daily.json <- fromJSON(states_daily.text, flatten = TRUE)
states_daily.df <- as.data.frame(states_daily.json)
states_daily.df <- states_daily.df %>% select(-one_of("hash"))

states_daily.df$date <- lubridate::ymd(states_daily.df$date)
states_daily.df$dateChecked <- states_daily.df$dateChecked %>% stringr::str_sub(start = 1, end = 10)
states_daily.df$dateChecked <- lubridate::ymd(states_daily.df$dateChecked)
```

Log scale plot **total positives** vs **positive increase** CA in red, IA in blue
```{r message=FALSE, warning=FALSE}
## plot CA vs. IA
states_daily.df %>% 
  filter(state == c("CA")) %>%
  ggplot(aes(positive, positiveIncrease)) + 
  geom_smooth(model = glm, color = "red") +
  geom_point(color = "red") +
  geom_smooth(data = states_daily.df %>% filter(state == "IA"),
              aes(positive, positiveIncrease),
              model = glm,
              color = "blue") +
  geom_point(data = states_daily.df %>% filter(state == "IA"), color = "blue") +
  theme_dark() +
  scale_x_continuous(trans = 'log10') +
  scale_y_continuous(trans = 'log10') +
  labs(title ="IA Blue, CA Red", x = "Postive Cases", y = "Increase")
```

The idea here is that the number of new cases is proportional to the number of cases. Thus, the slope the line should give us an indication of
